Comunicações Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-05-02 tese/section04.tex
added more on interactive recording

	Media Types can be described as discrete or continuos and interactive or non-interactive. For example an image is non-interctive and discrete, for instance, a video is continuos and non-interactive. A simple chat with just text is interactive and discrete. An animation that changes in function of user behaviour is interactive and continuous.

@@

	In order to play any kind of stream, a player for interactive stream is needed downloading an environment, decoding the \ac{RTP} payload to determine the state and display it to the user. Streaming interactive media like the combination of \ac{HTML}, \ac{CSS} and JavaScript requires more than interpreting the code, a streamed user interface may contain an internal state that is not shown on code.

@@

	To achieve synchronization of interactive data most packets have three types: State, Delta-State and Event. State packet defines environment's complete state. Delta-State packets tranports just the piece of state that changed. Event packets informs that an event ocurred over the interactive media.

@@

	If the \ac{RTP} recorder controls the correct data to send to the receivers, it cannot be a simple \ac{RTP} recorder as it must compute the state or delta-state to send. Therefore, if the receiver receives all recorded packets, it can calculate the current state from a nearest complete state. Having too much complete states, results on more precise random accesses but there is the storage space payback. On the other hand if there are few complete states recorded followed by delta-states, the recorded stream will occupy less storage space, but random accesses will be less granular.

@@

@@

  \cite{interactive_stream} proposed an \ac{RTP} profile for real-time transmission of interactive media. This new profile reuses much of video and audio profile implementation, integrating the interactive component.

>>>>

	Media Types can be distinguished by two criteria, the first one describes a media as discrete or continuos, the second one describes it as interactive or non-interactive. A discrete media is caracterized by its type not depending from time, as continuous media depending from it. Interactive media is caracterized by its state being changed by external events such as user interactions.

	For example, an image is non-interctive and discrete, for instance, a video is continuos and non-interactive. A simple colaborative editor with just text is interactive and discrete. An animation that changes in function of user behaviour is interactive and continuous.

@@

	In order to play any kind of stream, a player for interactive stream is needed for downloading an environment, decoding the \ac{RTP} payload to determine the state and display it to the user. Streaming interactive media like the combination of \ac{HTML}, \ac{CSS} and JavaScript requires more than interpreting the code, a streamed user interface may contain an internal state that is not shown on code.

@@

	To achieve synchronization of interactive data most packets have three types: \textit{State}, \textit{Delta-State} and \textit{Event}. State packet defines environment's complete state. Delta-State packets transports just the piece of state that changed. Event packets informs that an event ocurred over the interactive media.

@@

	If the \ac{RTP} recorder controls the correct data to send to the receivers, it cannot be a simple \ac{RTP} recorder as it must compute the state or delta-state to send. Therefore, if the receiver receives all recorded packets, it can calculate the current state from a nearest complete state. Streaming too much complete states, results on more precise random accesses but the trade-off is the higher bandwidth usage and used storage space on the recording server. On the other hand, if there are fewer complete states recorded followed by delta-states, the recorded stream will occupy less storage space, but random accesses will be less granular.

@@

	In order to synchronize an interactive application state amongst participants, the needed objects to synchronize must be serializable and sent to other participants.

@@

  \cite{interactive_stream} proposed an \ac{RTP} profile for real-time transmission of interactive media. This new profile reuses much of video and audio profile implementation, integrating the interactive component.   \cite{interactive_record} explained how to record interactive video with this new profile.
